Variational Monte Carlo on Bosonic Systems

### 2018-04-06 project_1/article/article.tex
Spell check section on finding the minimum

            For this optimal, interacting $\alpha$ we have computed the expected
            energy and standard deviation for systems of $n = \{10, 50, 100\}$
            particles. These results are shown in \autoref{tab:10_optimal}, the
            non-interacting case, excluding Jastrow factor is included as a
            comparison.

@@

@@

            \begin{table}
                \caption{Comparison of the elliptical system with an elliptical
                gaussian trial wavefunction with and without the Jastrow
                factor.}
                \centering
                \begin{ruledtabular}
                    \begin{tabular}{r|rr|rr}
                        & \multicolumn{2}{c|}{Interacting}
                        & \multicolumn{2}{c}{Non-interacting} \\
                        \hline
                        $N$ & $\expval{E}$ & $\sigma_b$ & $\expval{E}$
                        & $\sigma_b$ \\
                        \hline
                        10 & 24.3986 & 0.0003 & 24.1418 & 0.0002 \\
                        50 & 127.2852 & 0.0077 & 120.7129 & 0.0012 \\
                        100 & 266.2904 & 0.0297 & 241.4248 & 0.0025
                    \end{tabular}
                \end{ruledtabular}
                \label{tab:10_optimal}
            \end{table}

@@

    \subsection{Low density system}
        It is safe to say that the effect of adding a Jastrow factor is significant,
        i.e. the increase in
            energy for the system as the interaction is switched on is much higher
            than the uncertainty of the energy. A simple look at \autoref{fig:interacting}
            will be proof enough as the error bars of the figure are not discernible.
        On the other hand, the energy added to the system by including interaction
        is not very high compared to the energy of the system as a whole. For the
        larger of the interacting systems we have looked at, with $n=100$ particles,
        The interaction add only a mere $9\%$ extra energy (see \autoref{tab:10_optimal}).
        Studying \autoref{fig:one_body_density_100} will reveal the same.

>>>>

            For this value of $\alpha$ we have computed the expected energy and
            standard deviation for systems of $N = \{10, 50, 100\}$ particles.
            These results are shown in \autoref{tab:interacting_optimal}. We have
            compared with the non-interacting case, i.e., where the Jastrow
            factor is zero ($a = 0$).

@@

            \begin{table}
                \caption{Comparison of an elliptical gaussian trial wavefunction
                with and without the Jastrow factor using the elliptical trap.}
                \centering
                \begin{ruledtabular}
                    \begin{tabular}{r|rr|rr}
                        & \multicolumn{2}{c|}{Interacting}
                        & \multicolumn{2}{c}{Non-interacting} \\
                        \hline
                        $N$ & $\expval{E}$ & $\sigma_b$ & $\expval{E}$
                        & $\sigma_b$ \\
                        \hline
                        10 & 24.3986 & 0.0003 & 24.1418 & 0.0002 \\
                        50 & 127.2852 & 0.0077 & 120.7129 & 0.0012 \\
                        100 & 266.2904 & 0.0297 & 241.4248 & 0.0025
                    \end{tabular}
                \end{ruledtabular}
                \label{tab:interacting_optimal}
            \end{table}

@@

@@

    \subsection{Low density system}
        It is safe to say that the effect of adding a Jastrow factor is significant,
        i.e. the increase in
            energy for the system as the interaction is switched on is much higher
            than the uncertainty of the energy. A simple look at \autoref{fig:interacting}
            will be proof enough as the error bars of the figure are not discernible.
        On the other hand, the energy added to the system by including interaction
        is not very high compared to the energy of the system as a whole. For the
        larger of the interacting systems we have looked at, with $n=100$ particles,
        The interaction add only a mere $9\%$ extra energy (see \autoref{tab:interacting_optimal}).
        Studying \autoref{fig:one_body_density_100} will reveal the same.
